Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/experiments.tex
Work on prediction
Add latest results tables.

\input{../figs/results-llk2.tex}

@@

[TODO: Recall table.]

[TODO: Mention that we cap the value of $K$]

[TODO: Discuss results.]
%\input{../figs/results-recall.tex}

>>>>

\input{../figs/results-llk3.tex}
\input{../figs/results-recall-5.tex}
\input{../figs/results-recall-20.tex}

@@

In order to investigate the role of the number of clusters, $K$, we introduce an upper bound on the number of clusters during the fitting process.  In Table ~\ref{tab:results} we compare the loglikelihood on held-out test data while varying the maximum allowed $K$.  A relational event model (i.e. our model with $K=1$) outperforms the baselines on these data sets.  For the synthetic data example introduced in Section \ref{sec:simulation} the fitted models with $K>1$ have predictive performance comparable to the true model; a standard relational event model does not perform as well because it does not have the flexibility to model the dynamics of each block separately.  For the classroom data set we see only a slight improvement with $K>1$, while with the mobile phone calls the $K=3$ model performs best.
In Table~\ref{tab:recall5} and Table~\ref{tab:recall20} we include the corresponding results for the recall experiment at a cutoff of 5 and 20, respectively.  The results there are similar.
